\documentclass[a4paper,oneside]{memoir}

\usepackage[T1]{fontenc}
\usepackage{accanthis}

%% \usepackage[T1]{fontenc}
%% \usepackage{Alegreya} %% Option 'black' gives heavier bold face 
%% \renewcommand*\oldstylenums[1]{{\AlegreyaOsF #1}}

%% \usepackage{concmath}
%% \usepackage[T1]{fontenc}

%% \usepackage{caladea}
%% \usepackage[T1]{fontenc}

%% \usepackage[default]{cantarell} %% Use option "defaultsans" to use cantarell as sans serif only
%% \usepackage[T1]{fontenc}

%% \usepackage[bitstream-charter]{mathdesign}
%% \usepackage[T1]{fontenc}

%% \usepackage[defaultsans]{droidsans}
%% \renewcommand*\familydefault{\sfdefault} %% Only if the base font of the document is to be typewriter style
%% \usepackage[T1]{fontenc}

%% \usepackage{epigrafica}
%% \usepackage[LGR,OT1]{fontenc}

%% \usepackage{fetamont}
%% \usepackage[T1]{fontenc}

%% \usepackage[T1]{fontenc}
%% \usepackage[default]{gillius}

\usepackage[margin={3cm,3cm}]{geometry}  % influences column width
\usepackage{multicol}
\usepackage{lipsum}
\usepackage{titling}
\usepackage[usenames,dvipsnames]{xcolor}					% color
\usepackage{url}
\usepackage{tikz}

\pagenumbering{gobble} % no page numbers
\setlength{\parindent}{0pt}			% no paragraph indentation

\usepackage{fourier-orns}

\newcommand{\ornamento}{\vspace{2em}\noindent \textcolor{darkgray}{\hrulefill~ \raisebox{-2.5pt}[10pt][10pt]{\leafright \decofourleft \decothreeleft  \aldineright \decotwo \floweroneleft \decoone   \floweroneright \decotwo \aldineleft\decothreeright \decofourright \leafleft} ~  \hrulefill \\ \vspace{2em}}}

\setlength{\droptitle}{-0.7cm}
\pretitle{\Huge}
\posttitle{\normalsize\normalfont\hspace{\stretch{1}}}
\preauthor{\Large\center}
\postauthor{\hspace{\stretch{3}}}
\predate{}
\postdate{}
% \usepackage[xcolor]{rvdtx}

\columnsep=40pt
\title{Eden Cardim}
\author{IT Consultant}

\begin{document}
\maketitle
%\contact{edencardim@gmail.com}
%\version{1.0}
%\date{2016/03/02}
%\keywords{\LaTeX, grid typesetting}

\tikz{%
	\draw[dotted,thick,color=RoyalBlue,yshift=0]
	(0,0) -- (\textwidth,0);}%

\begin{multicols}{2}
\begin{flushright}
\Large\textbf{\color{RoyalBlue}\uppercase{Profile}}\normalsize\scriptsize\\

I have been developing software and administering systems since 1998 and have
collaborated with several open source projects. I also specialize in planning
and developing both relational and big data database architectures with cloud
computing.\\

I'm concerned with social awareness, equality and sustainability, most of my
volunteer efforts are geared towards social improvement and climate change.\\

\normalsize

\vspace{1em}

\Large\textbf{\color{RoyalBlue}\uppercase{Contact}}\normalsize\\


edencardim@gmail.com\\
https://github.com/edenc\\

+55 11 9 9644 8225\\
\vspace{1em}
\scriptsize
Rua Almirante Brasil, 243\\
Ap. 132C\\
Mooca, SP\\
Brasil\\
\normalsize

\vspace{1em}

\Large\textbf{\color{RoyalBlue}\uppercase{Skills}}\normalsize\\
\footnotesize\textbf{
    \begin{tabular*}{132pt}{rrr}
      Perl & Javascript & SQL\\
      C & C++ & R\\
      Java & Haskell & Prolog\\
      Python & Ruby & LISP\\
      \LaTeX & PostgreSQL & MySQL\\
      Apache & Hadoop & Git\\
      Linux & FreeBSD & Windows\\
    \end{tabular*}
}

\normalsize

\vspace{1em}
\Large\textbf{\color{RoyalBlue}\uppercase{Languages}}\normalsize\\

native
\textbf{Portuguese}\\

fluent
\textbf{English}\\

mostly reading
\textbf{Spanish}\\

\vspace{1em}
\Large\textbf{\color{RoyalBlue}\uppercase{Education}}\normalsize\\
\textbf{Universidade Estadual de Santa Cruz}\normalsize\\
Computer Science BSc.\\

\vspace{1em}

\Large\textbf{\color{RoyalBlue}\uppercase{Publications}}\normalsize\\
\textbf{The Definitive Guide to Catalyst - 2009}\\
\scriptsize
Apress\\
Kieren D., Matt T., Eden C., Jay K., Jess R.\\
ISBN-13 978-1430223658\\
ISBN-10 1430223650\\
\normalsize
\vspace{1em}
\Large\textbf{\color{RoyalBlue}\uppercase{Awards \& Honors}}\normalsize\\
\textbf{Desarollando America Latina - 2011}\\

\scriptsize

Won the first edition of the \emph{Desarollando America Latina} hackathon by
implementing the \emph{Onde Acontece} application, facing competition of 18
teams from countries across Latin America.\\

\normalsize
\vspace{1em}
\Large\textbf{\color{RoyalBlue}\uppercase{Extra-Curricular Activities}}\normalsize\\
\textbf{Google Summer of Code - 2011}\\
\scriptsize

Voluntary mentor involving the improvement of Catalyst's dependency injection
mechanism.\\

\normalsize

\textbf{São Paulo Perl Workshop - 2011}
\scriptsize
Speaker
\normalsize\\

\textbf{FISL - 2008, 2009}
\scriptsize
Speaker
\normalsize\\

\textbf{CONISLI - 2008}
\scriptsize
Speaker
\normalsize\\

\end{flushright}

\columnbreak

\begin{flushleft}

\Large\textbf{\color{RoyalBlue}\uppercase{Experience}}\normalsize

\textbf{\color{RoyalBlue}Tata Consulting Services} \footnotesize São Paulo, Brazil\normalsize

\textbf{BI Analyst}
\footnotesize\textbf{Mar 2016 -- Present}\normalsize

\textbf{\color{RoyalBlue}IBM} \footnotesize São Paulo, Brazil\normalsize

\textbf{Database Analyst}
\footnotesize\textbf{Jul 2014 -- Mar 2016}\normalsize

\scriptsize
Design database architectures for both big data and relational database systems.
Demonstrate capacity to potential clients during the pre-sales phase then
deliver and deploy solutions at the client site.

\normalsize

\textbf{\color{RoyalBlue}urby.com.br} \footnotesize São Paulo, Brazil\normalsize

\textbf{Technical Director}
\footnotesize\textbf{Jun 2013 -- Jul 2014}\normalsize

\scriptsize

Design IT architecture and infrastructure solutions applied to geocomputation.
Support development teams on design decisions. Hands-on development with
Javascript, Perl, PostgreSQL and PostGIS.

\normalsize

\textbf{\color{RoyalBlue}Insolide IT} \footnotesize São Paulo, Brazil\normalsize

\textbf{CTO}
\footnotesize\textbf{Jun 2013 -- Jul 2014}\normalsize

\scriptsize
Negotiate contracts with customers, project management and hands-on development
with Perl, Ruby, PostgreSQL, Apache and Amazon Web Services.

\footnotesize\textbf{\color{RoyalBlue}Clients/Projects}\\
\textbf{Instituto Ruth Cardoso}\\
\textbf{Estante Virtual}\\

\normalsize

\textbf{\color{RoyalBlue}Shadowcat Systems Ltd.} \footnotesize Lancaster, UK\normalsize

\textbf{Lead Developer}
\footnotesize\textbf{Jan 2008 -- Aug 2013}\normalsize

\scriptsize

Database/Software design and implementation, project management and
Catalyst/DBIx::Class scalability solutions for high-traffic websites. Built
tailor-made Business Intelligence tools for customers.

\footnotesize\textbf{\color{RoyalBlue}Clients/Projects}\\
\textbf{University of Indiana}\\
\textbf{Cisco Systems Inc.}\\
\textbf{US Census}\\
\textbf{British Broadcasting Company}\\
\textbf{Takkle Inc.}\\
\textbf{Socialflow Inc.}\\

\normalsize

\textbf{\color{RoyalBlue}IonZero LLC} \footnotesize Fort Collins, USA\normalsize

\textbf{Software Developer}
\footnotesize\textbf{Aug 2010 -- Dec 2010}\normalsize

\scriptsize

OLAP solutions and operations for various customers.

\normalsize

\textbf{\color{RoyalBlue}DBIX Corp.} \footnotesize San Francisco, USA\normalsize

\textbf{Software Developer}
\footnotesize\textbf{Feb 2008 -- May 2008}\normalsize

\scriptsize

Parsing/lexing solutions for domain-specific programming languages. Implemented
a Wiki from the ground up to demonstrate DSL capacities.

\normalsize

\textbf{\color{RoyalBlue}PictureTrail Inc.} \footnotesize Silicon Valley, USA\normalsize

\textbf{Software Developer}
\footnotesize\textbf{Jun 2007 -- Dec 2007}\normalsize

\scriptsize

Scalability solutions and software design for Catalyst-based web applications.

\normalsize

\textbf{\color{RoyalBlue}Núcleo de Biologia Computacional e Gestão de Informações Biotecnológicas da Bahia} \footnotesize Ilhéus, Brazil\normalsize

\textbf{Researcher}
\footnotesize\textbf{Feb 2005 -- Aug 2007}\normalsize

\scriptsize

Bioinformatics applied to research on the \emph{Moniliophthora roreri} genome.
Designed and implemented genomics analysis tools, annotation and processing
workflows.

\normalsize

\textbf{\color{RoyalBlue}Vapt Net} \footnotesize Ipiaú, Brazil\normalsize

\textbf{Systems Administrator}
\footnotesize\textbf{Jan 1998 -- Jan 1999}\normalsize

\scriptsize

Linux administration and support. Development of the corporate ticket portal.

\end{flushleft}

\end{multicols}

\end{document}

% End of document.
